### 2022-09-08 README.Rmd
Updates
Readme updates

# simbased

@@

The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `sim_plot()`. These work together to create a simple workflow for simulation-based inference.

* `sim()` simulates model parameters from a fitted model
* `sim_apply()` applies an estimator to the simulated coefficients, or to the original object but with the new coefficients inserted
* `summary()` produces confidence intervals and p-values for the resulting estimates
* `sim_plot()` produces plots of the simulated sampling distribution of the resulting estimates

@@

#Plot the resulting sampling distributions
sim_plot(sim_est)
```

@@

#Plot of predicted values across age for each value of treat
setx_plot(sim_est)
```

>>>>

# `simbased`: Simulation-Based Inference for Regression Models

@@

The `simbased` package was designed to provide a simple, general interface to simulation-based inference, along with a few convenience functions to perform common tasks like computing average marginal effects. The primary functions of `simbased` are `sim()`, `sim_apply()`, `summary()`, and `plot()`. These work together to create a simple workflow for simulation-based inference.

* `sim()` simulates model parameters from a fitted model
* `sim_apply()` applies an estimator to the simulated coefficients, or to the original object but with the new coefficients inserted
* `summary()` produces confidence intervals and p-values for the resulting estimates
* `plot()` produces plots of the simulated sampling distribution of the resulting estimates

@@

#Plot the resulting sampling distributions
plot(sim_est)
```

@@

#Plot of predicted values across age for each value of treat
plot(sim_est)
```
